\documentclass{alggeom}

\input{HeaderFile.tex}

\begin{document}

\title{\bf Integral cohomology of the generalized\\Kummer fourfold}


\author{Simon Kapfer}
\email{simon.kapfer@math.uni-augsburg.de}
\address{Institute of Mathematics of Augsburg university, D--86159 Augsburg, Germany}
\author{Gr\'egoire Menet}
\email{menet@ime.unicamp.br}
\address{University of Campinas, Institudo de Matematica estatistica e Camputa\c{c}ao Cientifica, Cx. Postal 6065 - CEP 13083-970-Campinas-SP, Brazil}
%\address{Simon Kapfer, Institut f\"ur Mathematik, Universit\"at Augsburg, D--86159 Augsburg}
%\email{simon.kapfer@math.univ-poitiers.fr}
%\email{simon.kapfer@math.uni-augsburg.de}
%\urladdr{http://www.math.uni-augsburg.de/alg/}
\classification{14J17, 14J35, 14F43.}
\keywords{Integral cohomology, generalized Kummer fourfolds, Nakajima operators, 
irreducible symplectic V-manifolds, Beauville--Bogomolov form.}

%\date{\today}
\begin{abstract}
We describe the integral cohomology of the generalized Kummer fourfold giving an explicit basis, using Hilbert scheme cohomology and tools developed by Hassett and Tschinkel.
Then we apply our results to a IHS variety with singularities, obtained by a partial resolution of the generalized Kummer fourfold quotiented by a symplectic involution. 
We calculate the Beauville--Bogomolov form of this new variety, presenting the first example of such a form that is odd.
\end{abstract}
\maketitle



\input{Introduction.tex}
%\part{Preliminaries}
%\input{Section_Lattices.tex}
%\input{Section_Recall_Integral}
\input{Section_OddH2.tex}
\input{Section_Hilbert.tex}
%\part{The Generalized Kummer fourfold}\label{integralcohomology}
\input{Section_GeneralKummer.tex}
%\input{Section_Kummer4.tex}
\input{Section_H4.tex}
\input{SummaryKummerFourfold.tex}
%\part{A quotient}\label{quotient}
%\section{Symplectic involution on a $\kum{A}{2}$-type ISM}
%\section{$H^4$-normality and $H^2$-normality}
%\section{On $H^2(K,\Z)$}
%\section{Calculation of the Beauville-Bogomolov form}
\input{ApplicationKummer}
\appendix
\input{Appendix.tex}
\begin{acknowledgements}
We want to thank Samuel Boissi\`ere, David Chataur, Brendan Hassett, Giovanni Mongardi, Marc Nieper-Wi\ss kirchen and Ulrike Rie\ss\ for useful discussions.
We also thank Samuel Boissi\`ere, Daniel Huybrechts and Marc Nieper-Wi\ss kirchen for hospitality.
%We want to thank Samuel Boissi\`ere, Daniel Huybrechts and Marc Nieper-Wi\ss kirchen for their kind support during the development of the project.
%We also thank Brendan Hassett and Giovanni Mongardi for useful discussions.
GM is supported by Fapesp grant 2014/05733-9. SK was partially supported by a DAAD grant.
\end{acknowledgements}
\input{Bibliography.tex}

\end{document}
