\bibliographystyle{amsplain}
\begin{thebibliography}{10}

\bibitem{Beauville}
A.~Beauville, \emph{Vari\'et\'es k\"ahleriennes dont la premi\`ere classe de Chern est nulle}, 
  J. Differential geometry 18 (1983) 755--782.

\bibitem{Boissiere}
S.~Boissi\`ere, \emph{Chern classes of the tangent bundle on the Hilbert scheme of points
  on the affine plane}, J.~Algebraic Geom. \textbf{14} (2005), no.~14, 761--787.

\bibitem{BCS}
S.~Boissi\`ere, C.~Camere and A.~Sarti, \emph{Classification of automorphisms on a deformation family of hyperk\"ahler
fourfolds by $p$-elementary lattices}, arXiv:1402.5154v1.

\bibitem{Generating}
S.~Boissi\`ere and M.~Nieper-Wi{\ss}kirchen, \emph{Generating series in the cohomology 
  of Hilbert schemes of points on surfaces}, LMS J.~of Computation and Math.~10 (2007), 254--270 .

\bibitem{BNS2}
S.~Boissi\`ere, M. Nieper-Wisskirchen and A. Sarti, 
\emph{Higher dimensional Enriques varieties and automorphisms of generalized Kummer varieties},
Journal de Math\'ematiques Pures et Appliqu\'ees,
vol. 95 (2011), no. 5 553--563.

\bibitem{BNS}
S.~Boissi\`ere, M.~Nieper-Wi{\ss}kirchen, and A.~Sarti, \emph{Smith theory and 
  Irreducible Holomorphic Symplectic Manifolds}, Journal of Topology 6 (2013), no.~2, 361--390.

\bibitem{Borcea}
C.~Borcea,
\emph{Diffeomorphisms of a K3 surface},
Math. Ann., 275(1):1--4, 1986.

\bibitem{Bredon}
G.E.~Bredon,
\newblock \emph{Intoduction to compact transformation groups},
Academic Press, New York,
(1972), Pure and Applied Mathematics, Vol. 46.

\bibitem{Britze} 
M.~Britze, \emph{On the cohomology of generalized Kummer varieties}, PhD thesis of Cologne University (2003) 

\bibitem{DeligneMorgan}
P.~Deligne and J.~Morgan, \emph{Notes on supersymmetry (following Joseph Bernstein)}, Quantum
fields and strings: a course for mathematicians, Vol. 1, 2 (Princeton, NJ, 1996/1997), 41--97,
Amer. Math. Soc., Providence, RI (1999).

\bibitem{Dolgachev}
Igor V.~Dolgachev, \emph{Classical Algebraic Geometry}, 
  Cambridge University Press (2012).

\bibitem{Farb}
B.~Farb and D.~Margalit \emph{A primer on mapping class groups}, Princeton University Press.

\bibitem{Fogarty}
J.~Fogarty, \emph{Algebraic Families on an Algebraic Surface},
  Am.~J.~Math.~\textbf{10} (1968), 511--521.

\bibitem{FujikiK}
A.~Fujiki,
\emph{A theorem on bimeromorphic maps of K\"ahler manifolds and its applications},
Publ. Res. Inst. Math. Sci., 
17(2): 735--754, 1981.

\bibitem{Fujiki}
A.~Fujiki, \emph{Finite automorphism groups of complex tori of dimension two}, Publ. RIMS,
  Kyoto Univ., \textbf{24} (1988), 1-97.

\bibitem{Fujiki2}
A.~Fujiki,
\emph{On Primitively Symplectic Compact K\"ahler V-manifolds of Dimension Four},
Classification of algebraic and analytic manifolds, 
(Katata, 1982), 71-250.

\bibitem{Fulton}
W.~Fulton,
\emph{Intersection theory},
Second edition, Springer.

\bibitem{Ghys}
E.~Ghys and A.~Verjovsky, \emph{Locally free holomorphic actions of the complex affine group},
  Geometric Study of Foliations, World Scientific (1994), 201--217.

\bibitem{Gottsche}
L.~G\"ottsche, \emph{Hilbert Schemes of Zero-Dimensional Subschemes of Smooth Varieties},
  Lecture Notes in Mathematics 1572, Springer (1994).

\bibitem{Hassett}
B.~Hassett and Y.~Tschinkel, \emph{ Hodge theory and Lagrangian planes on 
  generalized Kummer fourfolds}, Moscow Math. Journal, 13, no. 1, 33--56, (2013) 

\bibitem{Huybrechts2}
D.~Huybrechts,
\emph{ Compact hyperk\"ahler manifolds: basic results},
Invent. math. 
135, 63-113 (1999).

\bibitem{Tim}
T.~Kirschner, 
\emph{Irreducible symplectic complex spaces},
PhD thesis, arXiv:1210.4197.
  
\bibitem{Kapfer}
S.~Kapfer, \emph{Symmetric Powers of Symmetric Bilinear Forms, Homogeneous Orthogonal Polynomials 
  on the Sphere and an Application to Compact Hyperk\"ahler Manifolds} arXiv:1507.00157.
  
\bibitem{LehnSorger}
M.~Lehn and C.~Sorger, \emph{The cup product of Hilbert schemes for {$K3$}
  surfaces}, Invent. Math. \textbf{152} (2003), no.~2, 305--329.

\bibitem{LiQinWang2}
W.~Li, Z.~Qin and W.~Wang, \emph{Hilbert schemes and W algebras} Int.~Math.~res.~Not. (2002),
  no. 27, 1427--1456.

\bibitem{LiQinWang}
---, \emph{Vertex algebras and the cohomology ring structure of 
  Hilbert schemes of points on surfaces} Math. Ann. 324 (2002), no. 1, 105--133.  
  
\bibitem{Markou}
D.~Markushevich, A.S.~Tikhomirov,
\emph{ New symplectic V-manifolds of dimension four via the relative compactified Prymian},
International Journal of Mathematics, Vol. 18, No. 10 (2007) 1187-1224,
World Scientific Publishing Company.  
  
\bibitem{Markmansurvey}
E.~Markman,
\emph{ A survey of Torelli and monodromy results for holomorphic-symplectic varieties},
Complex and differential geometry,
257-322, Springer Proc. Math., 8, Springer, Heidelberg, (2011).  
  
\bibitem{Markman}
E.~Markman, \emph{Integral generators for the cohomology ring of moduli spaces of
  sheaves over Poisson surfaces}, Adv. Math. \textbf{208} (2007), no.~2,
  622--646.

\bibitem{Markman2}
E.~Markman, \emph{Integral constraints on the monodromy group of the
  hyperk\"ahler resolution of a symmetric product of a {$K3$} surface},
  Internat. J. Math. \textbf{21} (2010), no.~2, 169--223.

\bibitem{Markmanou}
E.~Markman and S.~Mehrtra,
\emph{Hilbert schemes of K3 surfaces are dense in moduli},
arXiv:1201.0031v1.

\bibitem{Mat}
D.~Matsushita,
\emph{On base manifolds of Lagrangian fibrations},
Science China Mathematics (2014), 531-542.

\bibitem{Lol2}
G.~Menet,
\emph{Beauville--Bogomolov lattice for a singular symplectic variety of dimension 4},
Journal of pure and apply algebra (2014), 1455-1495.

\bibitem{Lol}
G.~Menet
\emph{Cohomologie enti\`ere et fibration lagrangiennes sur certaines vari\'et\'es holomorphiquement symplectiques singuli\`eres},
PhD thesis of Lille 1 University, (2014).

\bibitem{Milne}
J.~S.~Milne, \emph{Abelian Varieties (v2.00)}, Available at www.jmilne.org/math/ (2008)  

\bibitem{Milnor}
J.~Milnor, D.~Husem\"oller, \emph{Symmetric bilinear forms}, Ergebnisse der Mathematik
  und ihrer Grenzgebiete 73, Springer (1973).

\bibitem{Mongardi}
G.~Mongardi
\emph{Symplectic involutions on deformations of $K3^{[2]}$},
Cent. Eur. J. Math. 
10 (2012), no.4, 1472-1485.

\bibitem{MongWanTari}
G.~Mongardi, K\'evin Tari and Malte Wandel,
\emph{Automorphisms of generalised Kummer fourfolds},
arXiv:1512.00225v2. 

\bibitem{MongWanTari0}
G.~Mongardi, K\'evin Tari and Malte Wandel
\emph{Prime order automorphisms of abelian surfaces: a lattice-theoretic point of view},
arXiv:1506.05679v1. 

\bibitem{Mumford}
D.~Mumford, \emph{Abelian varieties}, Tata Institute of Fundamental Research Studies in Mathematics, 
  No.~5 (1970).

\bibitem{Nakajima}
H.~Nakajima, \emph{Heisenberg algebra and Hilbert schemes of points on
  projective surfaces}, Ann. of Math. (2) \textbf{145} (1997), no.~2, 379--388.

\bibitem{Nanikawa}
Y.~Namikawa,
\emph{Extension of 2-forms and symplectic varieties},
J. Reine Angew. Math. 
539 (2001), 123-147.

\bibitem{Lattice}
V.V.~Nikulin,
\emph{Integral symmetric bilinear forms and some of their applications},
Math. USSR Izv.
14 (1980), 103-167.

\bibitem{Oguiso}
K.~Oguiso,
\emph{No cohomologically trivial non-trivial automorphism of generalized Kummer manifolds},
arXiv:1208.3750.

\bibitem{QinWang}
Z.~Qin and W.~Wang, \emph{Integral operators and integral cohomology classes of
  {H}ilbert schemes}, Math. Ann. \textbf{331} (2005), no.~3, 669--692.

\bibitem{Rapagnetta}
A.~Rapagnetta,
\emph{On the Beauville form of the known irreducible symplectic varieties},
Math. Ann.
321 (2008), 77-95.

%\bibitem{Scattone}
%F.~Scattone, \emph{On the compactification of moduli spaces for algebraic K3 surfaces},
%  Memoirs of the American Mathematical Society (1987), Volume 70, Number 374.

\bibitem{Shioda}
T.~Shioda, \emph{The period map of abelian surfaces}, J. Fac. S. Univ.Tokyo 25 (1978), 47--59.

\bibitem{Spanier}
E.~Spanier, 
\emph{The homology of Kummer manifolds},
Proc. Amer. Math. Soc.
7, (1956), 155-160.

\bibitem{Tari}
K.~Tari, 
\emph{Automorphismes des vari\'et\'es de Kummer g\'en\'eralis\'ees},
PhD Thesis, Universit\'e de Poitiers (2015).

\bibitem{Totaro}
B.~Totaro, \emph{The integral cohomology of the Hilbert scheme of two points}, arXiv:1506.00968.

\bibitem{Voisin}
C.~Voisin, \emph{Hodge Theory and Complex Algebraic Geometry, I},
  Cambridge studies in advanced mathematics 76, Cambridge University Press (2002).

\end{thebibliography}
